Qualifying Examination Paper

### 2018-10-16 main.tex
181016-0830

@@

        \item Domain Transfer
        \begin{itemize}
            \item Domain-Adversarial Training of Neural Networks \cite{ganin2016domain}
            \item Image-to-Image Translation with Conditional GANs \cite{isola2017image}
        \end{itemize}

>>>>

(TBD) LAPGAN

As the appreciation and use of GAN-based approaches increased, it was observed that the structure design of the $G$ and $D$ models deserved reconsideration.  Radford, Metz, and Chintala \cite{DBLP:journals/corr/RadfordMC15} evaluated various model architectures and recommended a set of guidelines and constraints for $G$ and $D$ architectures that appeared to perform well in terms of stability, convergence, resolution, and depth of representation.  These guidelines describe a Deep Convolutional GAN (DCGAN) and are summarized as follows: (a) use convolution and fractional convolution layers with striding to achieve adaptive down-sampling ($D$) or up-sampling ($G$), respectively, rather than fixed/deterministic methods (i.e. max pooling), (b) use batch normalization between convolution layers to mitigate collapse or failure due to poor initialization or vanishing gradients, (c) avoid fully-connected layers, with the exception of the input to $G$ and the output of $D$, to help earlier convergence, and (d) use Rectifier Linear Unit (ReLU) activation for input and hidden layers in $G$, tanh for the output layer in $G$, and Leaky ReLU for all layers in $D$.  In addition to performance improvements, the authors demonstrate that $D$ is able to learn semantically-relevant features that are both explainable (via latent-space walk based validation) and usable (via feature-based supervised classification).  In fact, the extracted features from $D$ were so informative that they were able to discover associations between the input noise vector $Z$ and some features, and even modify the generated images (such as face rotation) using simple interpolation along the correct axis in $Z$-space.  The strong semantic learning power offered by DCGAN made it a strong candidate for enabling full unsupervised learning tasks such that the features learned by $D$ can be later explained and applied for re-use.

%In Machine Learning, and especially Computer Vision, domain variance between training and test data has been a long standing challenge.  The domain of a data set can be explained as components of the distribution that are invariant to class label, but unique to the data set as a whole, in contrast to other similar data sets.  Ganin et al. recognized that an adversarial approach known as a Domain Adversarial Neural Network (DANN) could be used to help improve Domain Adaption (DA).  Their adversarial approach essentially minimizes the loss with respect to the basic classification task, and maximizes the loss with respect to an adversarial model trying to distinguish between the training domain and a test domain.

Wtihin the theme of semantic learning and generation, several significant contributions were made during 2016 and 2017.  Pathak, Krahenbuhl, Donahue, Darrell, and Efros successfully used an adversarial approach to inpaint (fill in missing portions of) images with large extents of missing pixel data.  Their architecture was based on an encoder-decoder (TBD ref) combined with GAN.  In their approach, the encoder encodes both whole and masked (portions missing) images and $D$ tries to discriminate whole vs. masked, while $G$ generates the completed images, conditioned on the context. ...

 serves as $G$, attempting to reconstruct the context encoding from images with missing portions and the decoder feeds $D$ which tries to distinguish between reconstructed images and complete images.  Interestingly, and in contrast with \cite{mirza2014conditional}, the authors achieved better results when $G$ was conditioned

@@

        \item Domain Transfer
        \begin{itemize}
            %\item Domain-Adversarial Training of Neural Networks \cite{ganin2016domain} - ADVERSARIAL BUT NOT GAN
            \item Image-to-Image Translation with Conditional GANs \cite{isola2017image}
        \end{itemize}
